---
title: "Porfolio 7 - Graphing Study 2"
author: "Adam"
date: "5/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> The goal of this portfolio is to create graphs to display the findings from Study 2.

## Setting up

```{r packages, echo=TRUE, message=FALSE}
library('reshape2')
library('ggplot2')
library('dplyr')
library('Rcpp')
library('readr')
library('tidyverse')
library('psych')
library('emmeans')
```

#### Bringing in the data

```{r loading data, echo=TRUE, collapse=TRUE, message=FALSE}
study1 <- read_csv("Study2_data_R_cleaned.csv")

# Ensuring the dataframe is a tibble.
as_tibble(study1)

#Taking a look at the table.
View(study1)
```

The code below subsets the data that I'm working with only to the parts I'm interested in. As well, it renames the condition variable to be easier to understand, and ensures that it is a factor.

```{r smaller data to work with}
study1_graph <- study1 %>%
        select(class_belong_comp4, school_belong_comp4, motiv_intrins_comp2, motiv_util_comp3, close_comp3, quiz_average,  condition)

study1_graph$condition = factor(study1_graph$condition,
                                levels = c(0,1,2),
                                labels = c("Control", "Prompted discussion", "Prompted disclosure")
                                )
```

### Creating graphs

I want to create bar graphs for each of the variables of interest. We created graphs that I used for my thesis, so my goal is going to be to recreate those. Specifically; Closeness, Institutional belonging, Class belonging, Intrinsic motivation, Utility motivation, and Quiz performance.

I will be using a lot of code in my graphs, so I've gone and made some shortcuts to plug in as I go. This idea was taken from the Youtube channel "Statistics of Doom". The point is to save me a lot of extra code typing that I could mess up, and to make the code look a little nicer.

```{r graph formatting code}
vis_col =   
  scale_fill_manual(values = c( #Color codes for the conditions.
    "Control" = "#fece3d",
    "Prompted discussion" = "#fd8d3c",
    "Prompted disclosure" = "#31a354"))

vis_theme =  theme(panel.background = element_blank(), #makes the background invisible
                   panel.grid.major.y = element_line(color = "#DAE1E7"), #makes the y-axis gridlines appear, but not x-axis
axis.line = element_line(color = "black")) #makes the axis appear in a dark black color

vis_text =     theme( #trbl are the margin signs, top, right, bottom, left
    plot.title = element_text(size = 20, margin = margin(b = 5)),
    plot.subtitle = element_text(size = 12, margin = margin(b= 10)),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 16, hjust = 1),    
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    axis.text.y = element_text(margin = margin(r = 5)),
    axis.text.x = element_text(margin = margin(t = 5)),
  )
```


#### Closeness

Below was the first successful version of the graph that I made. Very basic. Also, very wrong.

```{r first closeness graph}
ggplot(data = study1_graph, mapping = aes(x = condition, y= close_comp3)) +
  geom_bar(position= position_dodge(), stat= 'identity') 
```


After a lot of iteration, I got to this. The code is much more complex, and it pretty closely mirrors the graphs we actually used in my thesis. Explanations of the code are in-line.


```{r closeness graph}
ggplot(data = study1_graph, aes(x = condition, y= close_comp3, fill = condition)) + #Fill is starting the color code nonsense
  stat_summary(fun = mean, geom= "bar") + #This is making it measure the mean on the y-axis
  stat_summary(fun.data = mean_cl_normal, geom= "errorbar", width =.2, inherit.aes = TRUE)+ #mean_cl_normal and geom are making the error bars appear, inherit.aes makes it copy the aes from the beginning, e.g, fill
  guides(fill = FALSE) + # Allows the aes colors to be done manually.
  scale_y_continuous(limits = c(0, 5)) + #Affixes the scale to the full range of the measure
  vis_col + #This, vis_theme, and vis_text are shortcuts. See above.
  vis_theme + 
  labs(x = "Condition",
  y= NULL,
  title= "Closeness",
  subtitle= "Scale (1-5)") + # The terminology for the labels
  annotate("text", x="Control", y=1, label= "2.80", size=5) + #these lines add the means to the graph
  annotate("text", x= "Prompted discussion", y=1, label= "2.65", size=5) +
  annotate("text", x= "Prompted disclosure", y=1, label= "2.93", size=5) +
  vis_text
```

For the next graphs, I am wantonly stealing this code and making the modifications for each variable.

#### Institutional belonging

```{r institutional belonging code}
ggplot(data = study1_graph, mapping = aes(x = condition, y= school_belong_comp4, fill = condition)) + 
  stat_summary(fun = mean, geom= "bar") + 
  stat_summary(fun.data = mean_cl_normal, geom= "errorbar", width =.2, inherit.aes = TRUE)+ 
  guides(fill = FALSE) + 
  scale_y_continuous(limits = c(0, 7)) +
  vis_col + 
  vis_theme + 
  labs(x = "Condition",
  y= NULL,
  title= "School belonging",
  subtitle= "Scale (1-7)") + 
  annotate("text", x="Control", y=1, label= "5.34", size=5) +
  annotate("text", x= "Prompted discussion", y=1, label= "5.70", size=5) +
  annotate("text", x= "Prompted disclosure", y=1, label= "5.41", size=5) +
  vis_text
```


#### Class belonging

```{r class belonging code}
ggplot(data = study1_graph, mapping = aes(x = condition, y= class_belong_comp4, fill = condition)) + 
  stat_summary(fun = mean, geom= "bar") + 
  stat_summary(fun.data = mean_cl_normal, geom= "errorbar", width =.2, inherit.aes = TRUE)+ 
  guides(fill = FALSE) + 
  scale_y_continuous(limits = c(0, 7)) +
  vis_col + 
  vis_theme + 
  labs(x = "Condition",
  y= NULL,
  title= "Class belonging",
  subtitle= "Scale (1-7)") + 
  annotate("text", x="Control", y=1, label= "5.47", size=5) +
  annotate("text", x= "Prompted discussion", y=1, label= "6.08", size=5) +
  annotate("text", x= "Prompted disclosure", y=1, label= "5.49", size=5) +
  vis_text
```



#### Intrinsic motivation

```{r intrinsic motivation code}
ggplot(data = study1_graph, mapping = aes(x = condition, y= motiv_intrins_comp2, fill = condition)) + 
  stat_summary(fun = mean, geom= "bar") + 
  stat_summary(fun.data = mean_cl_normal, geom= "errorbar", width =.2, inherit.aes = TRUE)+ 
  guides(fill = FALSE) + 
  scale_y_continuous(limits = c(0, 5)) +
  vis_col + 
  vis_theme + 
  labs(x = "Condition",
  y= NULL,
  title= "Subject Area Motivation: Intrinsic",
  subtitle= "Scale (1-5)") + 
  annotate("text", x="Control", y=1, label= "3.45", size=5) +
  annotate("text", x= "Prompted discussion", y=1, label= "3.70", size=5) +
  annotate("text", x= "Prompted disclosure", y=1, label= "3.47", size=5) +
  vis_text
```

#### Utility motivation

```{r utility motivation code}
ggplot(data = study1_graph, mapping = aes(x = condition, y= motiv_util_comp3, fill = condition)) + 
  stat_summary(fun = mean, geom= "bar") + 
  stat_summary(fun.data = mean_cl_normal, geom= "errorbar", width =.2, inherit.aes = TRUE)+ 
  guides(fill = FALSE) + 
  scale_y_continuous(limits = c(0, 5)) +
  vis_col + 
  vis_theme + 
  labs(x = "Condition",
  y= NULL,
  title= "Subject Area Motivation: Utility",
  subtitle= "Scale (1-5)") + 
  annotate("text", x="Control", y=1, label= "3.27", size=5) +
  annotate("text", x= "Prompted discussion", y=1, label= "3.76", size=5) +
  annotate("text", x= "Prompted disclosure", y=1, label= "3.55", size=5) +
  vis_text
```

#### Quiz performance

This one required a change to the scale, since it is a grade, meaning the scale needed to run from 0 to .9

```{r intrinsic motivation code}
ggplot(data = study1_graph, mapping = aes(x = condition, y= quiz_average, fill = condition)) + 
  stat_summary(fun = mean, geom= "bar") + 
  stat_summary(fun.data = mean_cl_normal, geom= "errorbar", width =.2, inherit.aes = TRUE)+ 
  guides(fill = FALSE) + 
  scale_y_continuous(limits = c(0, .9)) +
  vis_col + 
  vis_theme + 
  labs(x = "Condition",
  y= NULL,
  title= "Quiz Performance",
  subtitle= "Scale (1-9)") + 
  annotate("text", x="Control", y=.20, label= "6.91", size=5) +
  annotate("text", x= "Prompted discussion", y=.20, label= "7.14", size=5) +
  annotate("text", x= "Prompted disclosure", y=.20, label= "7.12", size=5) +
  vis_text
```


#### Finishing up



